\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}

\begin{document}

\begin{center}
    {\Huge \textbf{Jane Smith}} \\
    \vspace{2mm}
    jane.smith@example.com $|$ linkedin.com/in/janesmithUX $|$ dribbble.com/janesmith
\end{center}

\vspace{5mm}

\section*{Summary}
\hrule
\vspace{2mm}
Highly creative and data-driven UI/UX Engineer with over 4 years of experience designing intuitive, accessible, and stunning digital interfaces. Expert in translating complex user flows into beautiful high-fidelity prototypes using Figma. Passionate about bridging the gap between visual design and front-end implementation.

\section*{Experience}
\hrule
\vspace{2mm}
\noindent \textbf{Senior UI/UX Designer} \hfill Creative Digital Agency (2021 - Present)
\begin{itemize}[leftmargin=*]
    \item Spearheaded the entire visual redesign of a flagship e-commerce platform, increasing user retention by 35\% utilizing Figma components and variants.
    \item Conducted comprehensive user research, A/B testing, and heuristic evaluations to inform design decisions and iterate on user flows.
    \item Established and maintained a robust scalable Design System in Figma to ensure visual consistency across web and mobile applications.
    \item Collaborated directly with frontend React engineers to hand off pixel-perfect spec files and interactive animations.
\end{itemize}

\vspace{3mm}

\noindent \textbf{UX Engineer} \hfill Innovative Startups LLC (2018 - 2021)
\begin{itemize}[leftmargin=*]
    \item Developed wireframes, user personas, and high-fidelity mockups for 12+ client applications ranging from fintech dashboards to healthcare portals.
    \item Built fully interactive prototypes in Figma emphasizing complex micro-interactions, responsive design constraints, and auto-layout.
    \item Converted initial design concepts into functional frontend components using HTML, CSS, and Tailwind.
\end{itemize}

\section*{Skills}
\hrule
\vspace{2mm}
\begin{itemize}[leftmargin=*]
    \item \textbf{Design Tools:} Figma, Adobe XD, Sketch, InVision, Zeplin, Miro
    \item \textbf{UX Methods:} User Research, Wireframing, Rapid Prototyping, Usability Testing, Information Architecture
    \item \textbf{Frontend:} HTML5, CSS3, Tailwind CSS, Basic React.js
    \item \textbf{Other:} Design Systems, Auto Layout, Accessibility (WCAG), Typography, Agile
\end{itemize}

\section*{Education}
\hrule
\vspace{2mm}
\noindent \textbf{Bachelor of Fine Arts in Interaction Design} \hfill Example School of Art, Class of 2018

\end{document}
